Microlensing as a possible probe of the internal structure of quasars

### 2015-07-17 paper1/fitting.tex
small correction

The crescent source had parameters (as explained in
\S\ref{subsec:crescent}) $R_p$ and $R_n$ being the radii of the outer
and inner circles and $(\alpha,\beta)$ being the coordinates of the inner
circle with respect to the centre of the outer circle in the coordinate system associated with
the image in figure 1 and not associated with the caustic surface as defined in the previous sections.  The parameter values were
\begin{equation}
   (R_p, R_n, $\alpha$, $\beta$) = (50.0, 30.0, 15.0, 10.0).
\label{eqn:cp}
\end{equation}
The uniform disc had the same (outer) radius as the crescent.  In the
Gaussian source, we set $3\sigma=50$.  For convenience, below we will
refer to $R_p$ of the Gaussian source, by which we actually mean
$3\sigma$.

>>>>

The crescent source had parameters (as explained in
\S\ref{subsec:crescent}) $R_p$ and $R_n$ being the radii of the outer
and inner circles and $(\alpha,\beta)$ being the coordinates of the inner
circle with respect to the centre of the outer circle in the coordinate system associated with the image in Figure 1 and not associated 
with the caustic surface as defined in the previous sections.  The parameter values were
\begin{equation}
   (R_p, R_n, $\alpha$, $\beta$) = (50.0, 30.0, 15.0, 10.0).
\label{eqn:cp}
\end{equation}
The uniform disc had the same (outer) radius as the crescent.  In the
Gaussian source, we set $3\sigma=50$.  For convenience, below we will
refer to $R_p$ of the Gaussian source, by which we actually mean
$3\sigma$.
